Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-06 paper.tex
Tabla del bandwidthtest modificada

The IPERF tool has been executed between the instances showed in 
the Table~\ref{table:iperf} in order to know the real bandwidth.
Therefore, we can assure that the nomenclature ''High'' used in the 
network column correspond to a 1Gb interconnection and the 10Gb has 
a real bandwidth of 7.5Gb/s.

>>>>

The IPERF tool has been executed between the instances showed in 
the Table~\ref{table:iperf} in order to know the real bandwidth.
Therefore, we can assure that the nomenclature ``High'' used in the 
network column correspond to a 1Gb interconnection and the 10Gb has 
a real bandwidth of 7.5Gb/s.
Moreover, it looks like the instances equipped with a ``High'' interconnection 
are software-limited up to 1 Gb/s due to the theoretical and real bandwith 
match perfectly. The gap between real and theorical can be observed with 
the 10Gb interconnection which reaches up to 7.5 Gb/s.
